Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-19 doc/report/evaluation.tex
adding files to the report
added some texts to the report, and a glass FSM figure
update evaluation

\section{Discussion}
\label{sec:discussion}

>>>>

\section{Evaluation}
\label{sec:evaluation}

\textcolor{red}{Will fill this evaluation when we get to it.}
Some of the ideas as to how to work on evaluation include: (A) Make a mobile (web) app that can remotely control the appliances through the gateway. Give a sequence of tasks to the tester and have him complete the tasks first on smartphone then use the Glass. (B) Observe the differences between using LED, Recon screen, and other feedbacks such as audio, and how that affects the user experience.
